---
title: "Enabling Environment"
output: html_document
---

```{r setup, include=FALSE}
setwd("C:/Users/crish/OneDrive/Documents/GitHub/BAI")

library(readr)
BAI <- readstata13::read.dta13("data/BAI.dta")

library(raster)
world_spdf <- shapefile("data/world_map/TM_WORLD_BORDERS_SIMPL-0.3.shp")

# Merge the BAI data to Shape Files
library(dplyr)
mapBAI <- world_spdf@data %>% left_join(BAI, by = c(ISO3 = "iso3"))
world_spdf@data <- mapBAI
```


```{r, include=FALSE}
library(leaflet)
bins3 <- c(0, 1, 2, 5, 100) 
pal4 <- colorBin(c("#C00000", "#FF6600", "#FFFF99", "#00B050"), domain = world_spdf$funding, bins = bins3)

```

### Increase funding for breastfeeding programmes

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.align='center'}
library(leaflet)
leaflet(world_spdf, width = 900) %>% 
  addTiles(urlTemplate = "//{s}.tiles.mapbox.com/v3/jcheng.map-5ebohr46/{z}/{x}/{y}.png",
        attribution = 'Maps by <a href="http://www.mapbox.com/">Mapbox</a>')  %>% 
  setView(lat=25, lng=2.8 , zoom=1.5) %>%

    # Data Layers
      # First Data Layer: 
    addPolygons(group="Funding for breastfeeding programs", data=world_spdf,
                color = "white", weight = 0.5, smoothFactor = 0.5, opacity = 1.0, fillOpacity = 1, 
                fillColor = ~pal4(funding),
                highlight = highlightOptions(weight = 2, color = "", dashArray = "1",
                                             fillOpacity = 0.6, bringToFront = TRUE),
                popup = paste(world_spdf$NAME,"<br/>",
                              "$", round(world_spdf$funding, 2), "<br/>")) %>%
  
  addLegend("bottomleft", 
  colors =c("#00B050", "#FFFF99", "#FF6600", "#C00000"),
  labels= c(">$5", "$2-5", "$1-2", "<$1"),
  title= "",
  opacity = 1)  %>%

  addEasyButton(easyButton(
    icon="fa-globe", title="Zoom to Entire World Map",
    onClick=JS("function(btn, map){ map.setZoom(1.5); }")))

```

```{r, include=FALSE}
library(leaflet)
bins4 <- c(0, 1.5, 2.5, 3.5, 4.5) 
pal5 <- colorBin(c("#C00000", "#FF6600", "#FFFF99", "#00B050"), domain = world_spdf$map_code, bins = bins4)

```


### Implement the International Code of Marketing of Breast-milk Substitutes and subsequent relevant World Health Assembly resolutions.

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.align='center'}
library(leaflet)
leaflet(world_spdf, width = 900) %>% 
  addTiles(urlTemplate = "//{s}.tiles.mapbox.com/v3/jcheng.map-5ebohr46/{z}/{x}/{y}.png",
        attribution = 'Maps by <a href="http://www.mapbox.com/">Mapbox</a>')  %>% 
  setView(lat=25, lng=2.8 , zoom=1.5) %>%

    # Data Layers
      # First Data Layer: 
    addPolygons(group="International Code", data=world_spdf,
                color = "white", weight = 0.5, smoothFactor = 0.5, opacity = 1.0, fillOpacity = 1, 
                fillColor = ~pal5(map_code),
                highlight = highlightOptions(weight = 2, color = "", dashArray = "1",
                                             fillOpacity = 0.6, bringToFront = TRUE),
                popup = paste(world_spdf$NAME,"<br/>",
                              world_spdf$code, "<br/>")) %>%
  
  addLegend("bottomleft", 
  colors =c("#00B050", "#FFFF99", "#FF6600", "#C00000"),
  labels= c("Full provisions in law", "Many provisions in law",
             "Few provisions in law", "No legal measures"),
  title= "",
  opacity = 1)  %>%

  addEasyButton(easyButton(
    icon="fa-globe", title="Zoom to Entire World Map",
    onClick=JS("function(btn, map){ map.setZoom(1.5); }")))

```
```{r, include=FALSE}
library(leaflet)
bins4 <- c(0, 1.5, 2.5, 3.5, 4.5) 
pal6 <- colorBin(c("#C00000", "#FF6600", "#FFFF99", "#00B050"), 
                 domain = world_spdf$map_compliance, 
                 bins = bins4)
```


### Adopt adequate maternity protection legislation in line with ILO Convention 183

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.align='center'}
library(leaflet)
leaflet(world_spdf, width = 900, height=550) %>% 
  addTiles(urlTemplate = "//{s}.tiles.mapbox.com/v3/jcheng.map-5ebohr46/{z}/{x}/{y}.png",
        attribution = 'Maps by <a href="http://www.mapbox.com/">Mapbox</a>')  %>% 
  setView(lat=25, lng=2.8 , zoom=1.5) %>%

    # Data Layers
      # First Data Layer: 
    addPolygons(group="Compliance", data=world_spdf,
                color = "white", weight = 0.5, smoothFactor = 0.5, opacity = 1.0, fillOpacity = 1, 
                fillColor = ~pal6(map_compliance),
                highlight = highlightOptions(weight = 2, color = "", dashArray = "1",
                                             fillOpacity = 0.6, bringToFront = TRUE),
                popup = paste(world_spdf$NAME,"<br/>",
                              world_spdf$compliance, "<br/>")) %>%
  
  addLegend("bottomleft", 
  colors =c("#00B050", "#FFFF99", "#FF6600", "#C00000"),
  labels= c("Meets ILO R191 standards", "Meets ILO C183 standards", 
            "Duration of leave is at least 14 weeks but other criteria for C183 are not clearly met", 
            "Duration of leave standard is not met"),
  title= "",
  opacity = 1)  %>%

  addEasyButton(easyButton(
    icon="fa-globe", title="Zoom to Entire World Map",
    onClick=JS("function(btn, map){ map.setZoom(1.5); }")))

```


```{r, include=FALSE}
library(leaflet)
bins5 <- c(-2, 0, 20, 50, 100) 
pal7 <- colorBin(c("#C00000", "#FF6600", "#FFFF99", "#00B050"), 
                 domain = world_spdf$map_baby, 
                 bins = bins5)

```


### Implement the Ten Steps to Successful Breastfeeding, with special focus on sick and vulnerable newborns

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.align='center'}
library(leaflet)
leaflet(world_spdf, width = 900) %>% 
  addTiles(urlTemplate = "//{s}.tiles.mapbox.com/v3/jcheng.map-5ebohr46/{z}/{x}/{y}.png",
        attribution = 'Maps by <a href="http://www.mapbox.com/">Mapbox</a>')  %>% 
  setView(lat=25, lng=2.8 , zoom=1.5) %>%

    # Data Layers
      # First Data Layer: 
    addPolygons(group="Babyfriendly", data=world_spdf,
                color = "white", weight = 0.5, smoothFactor = 0.5, opacity = 1.0, fillOpacity = 1, 
                fillColor = ~pal7(map_baby),
                highlight = highlightOptions(weight = 2, color = "", dashArray = "1",
                                             fillOpacity = 0.6, bringToFront = TRUE),
                popup = paste(world_spdf$NAME,"<br/>",
                              world_spdf$babyfriendly,"%", "<br/>")) %>%
  
  addLegend("bottomleft", 
  colors =c("#00B050", "#FFFF99", "#FF6600", "#C00000"),
  labels= c( ">50%", "20-50%", "1-20%", "None"),
  title= "",
  opacity = 1)  %>%

  addEasyButton(easyButton(
    icon="fa-globe", title="Zoom to Entire World Map",
    onClick=JS("function(btn, map){ map.setZoom(1.5); }")))

```


```{r, include=FALSE}
library(leaflet)
bins6 <- c(100, 75, 50, 25, 0) 
pal8 <- colorBin(c("#C00000", "#FF6600", "#FFFF99", "#00B050"), 
                 domain = world_spdf$counselling, bins = bins6)

pal9 <- colorBin(c("#C00000", "#FF6600", "#FFFF99", "#00B050"), 
                 domain = world_spdf$community_prog, bins = bins6)

```


### Improve access to qualified lactation support and strengthen linkages between health care and communities

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.align='center'}
library(leaflet)
leaflet(world_spdf, width = 900) %>% 
  addTiles(urlTemplate = "//{s}.tiles.mapbox.com/v3/jcheng.map-5ebohr46/{z}/{x}/{y}.png",
        attribution = 'Maps by <a href="http://www.mapbox.com/">Mapbox</a>')  %>% 
  setView(lat=25, lng=2.8 , zoom=1.5) %>%

    # Data Layers
      # First Data Layer: 
    addPolygons(group="Primary healthcare facilities providing IYCF counselling", data=world_spdf,
                color = "white", weight = 0.5, smoothFactor = 0.5, opacity = 1.0, fillOpacity = 1,
                fillColor = ~pal8(counselling),
                highlight = highlightOptions(weight = 2, color = "#666", dashArray = "1",
                                             fillOpacity = 0.6, bringToFront = TRUE),
                popup = paste(world_spdf$NAME,"<br/>",
                              round(world_spdf$counselling), "%", "<br/>")) %>%
    # Second Data Layer:
    addPolygons(group="Districts implementing community-based nutrition, health or other programmes with IYCF counselling", data=world_spdf,
                color = "white", weight = 0.5, smoothFactor = 0.5, opacity = 1.0, fillOpacity = 1,
                fillColor = ~pal9(community_prog),
                highlight = highlightOptions(weight = 2, color = "#666", dashArray = "1",
                                             fillOpacity = 0.6, bringToFront = TRUE),
                popup = paste(world_spdf$NAME,"<br/>",
                              round(world_spdf$community_prog), 
                              "% babies breastfed for the first 6 months", "<br/>")) %>%
  
  addLegend("bottomleft", pal = pal8, 
              values = ~counselling, title = "", opacity = 1) %>%
  
  addEasyButton(easyButton(
    icon="fa-globe", title="Zoom to Entire World Map",
    onClick=JS("function(btn, map){ map.setZoom(1.5); }"))) %>%

  # Layers control
    addLayersControl(
    #baseGroups = c("OpenStreetMap"),
    baseGroups = c("Primary healthcare facilities providing IYCF counselling", 
                   "Districts implementing community-based nutrition <br/> 
                   health or other programmes with IYCF counselling"),
    options = layersControlOptions(collapsed = FALSE) )

```

```{r, include=FALSE}
BAI$funding= round(BAI$funding,2)
BAI$counselling= round(BAI$counselling,2)
BAI$community_prog= round(BAI$community_prog,2)
```


###Table. Enabling environment indicators

```{r, echo=FALSE}
library(DT)
datatable(subset(BAI, select=c(region, country, funding, code, 
                               compliance, babyfriendly, counselling, community_prog)),
          colnames = c('Region', 'Country', 
                       'Donor Funding (USD) Per Live Birth', 
                       'Legal Status of the Code', 
                       'Compliance with C183 and R191', 
                       '% Births in Baby Friendly Hospitals and Maternities', 
                       '% Primary Healthcare Facilities with Individual IYCF Counselling', 
                       '% Districts Implementing Community Programs'), 
          filter = 'top', options = list(pageLength = 15, autoWidth = TRUE),
          caption = (''))

```

