---
title: "Practice"
output: html_document
---

```{r setup, include=FALSE}
setwd("C:/Users/crish/OneDrive/Documents/GitHub/BAI")

library(readr)
BAI <- readstata13::read.dta13("data/BAI.dta")

library(raster)
world_spdf <- shapefile("data/world_map/TM_WORLD_BORDERS_SIMPL-0.3.shp")

# Merge the BAI data to Shape Files
library(dplyr)
mapBAI <- world_spdf@data %>% left_join(BAI, by = c(ISO3 = "iso3"))
world_spdf@data <- mapBAI

```

## Improve breastfeeding outcome rates

Breastfed children have at least six times greater chance of survival in the early months than non-breastfed children.  An exclusively breastfed child is 14 times less likely to die in the first six months than a non-breastfed child, and breastfeeding drastically reduces deaths from acute respiratory infection and diarrhoea, two major child killers (Lancet 2008).

Select layer to see indicators on breastfeeding

```{r, include=FALSE}
library(leaflet)
bins <- c(100, 75, 50, 25, 0)
pal <- colorBin(c("#C00000", "#FF6600", "#FFFF99", "#00B050"), domain = world_spdf$bf_1hour, bins = bins)
```


```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.align='center'}
library(leaflet)
leaflet(world_spdf, width = 900) %>% 
  addTiles(urlTemplate = "//{s}.tiles.mapbox.com/v3/jcheng.map-5ebohr46/{z}/{x}/{y}.png",
        attribution = 'Maps by <a href="http://www.mapbox.com/">Mapbox</a>')  %>% 
  setView(lat=25, lng=2.8 , zoom=1.5) %>%

    # Data Layers
      # First Data Layer: 
    addPolygons(group="Breastfed within one hour", data=world_spdf,
                color = "gray", weight = 0.5, smoothFactor = 0.5, opacity = 1.0, fillOpacity = 1,
                fillColor = ~pal(bf_1hour),
                highlight = highlightOptions(weight = 2, color = "#666", dashArray = "1",
                                             fillOpacity = 0.6, bringToFront = TRUE),
                popup = paste(world_spdf$NAME,"<br/>",
                              round(world_spdf$bf_1hour), "% babies breastfed within one hour", "<br/>")) %>%
    # Second Data Layer:
    addPolygons(group="Breastfed for first 6 months", data=world_spdf,
                color = "white", weight = 0.5, smoothFactor = 0.5, opacity = 1.0, fillOpacity = 1,
                fillColor = ~pal(bf_6months),
                highlight = highlightOptions(weight = 2, color = "#666", dashArray = "1",
                                             fillOpacity = 0.6, bringToFront = TRUE),
                popup = paste(world_spdf$NAME,"<br/>",
                              round(world_spdf$bf_6months), 
                              "% babies breastfed for the first 6 months", "<br/>")) %>%
  
    # Third Data Layer:
    addPolygons(group="Breastfed at 1 year", data=world_spdf,
                color = "white", weight = 0.5, smoothFactor = 0.5, opacity = 1.0, fillOpacity = 1,
                fillColor = ~pal(bf_1yr),
                highlight = highlightOptions(weight = 2, color = "#666", dashArray = "1",
                                             fillOpacity = 0.6, bringToFront = TRUE),
                popup = paste(world_spdf$NAME,"<br/>",
                              round(world_spdf$bf_1yr), 
                              "% children still breastfed at 1 year of age", "<br/>")) %>%

      # Fourth Data Layer:
    addPolygons(group="Breastfed at 2 years", data=world_spdf,
                color = "white", weight = 0.5, smoothFactor = 0.5, opacity = 1.0, fillOpacity = 1,
                fillColor = ~pal(bf_2yr),
                highlight = highlightOptions(weight = 2, color = "#666", dashArray = "1",
                                             fillOpacity = 0.6, bringToFront = TRUE),
                popup = paste(world_spdf$NAME,"<br/>",
                              round(world_spdf$bf_2yr), "% children still breastfed at 2 years of age", "<br/>")) %>%
  
  addLegend("bottomleft", pal = pal, 
              values = ~bf_1hour, title = "", opacity = 1) %>%
  
  addEasyButton(easyButton(
    icon="fa-globe", title="Zoom to Entire World Map",
    onClick=JS("function(btn, map){ map.setZoom(1.5); }"))) %>%

  # Layers control
    addLayersControl(
    #baseGroups = c("OpenStreetMap"),
    baseGroups = c("Breastfed within one hour", 
                      "Breastfed for first 6 months", 
                      "Breastfed at 1 year", 
                      "Breastfed at 2 years"),
    options = layersControlOptions(collapsed = FALSE) )
```




```{r, include=FALSE}
library(readxl)
regional <- read_excel("C:/Users/crish/OneDrive/Documents/GitHub/BAI/data/regional.xlsx")
regional <- as.data.frame(regional)
#x<-regional[regional$indicator, regional$bf_1hour]

library(ggplot2)
library(plotly) 
plot_ly(regional, y = ~indicator, x=~bf_1hour, 
                     color = ~region, type = "bar",
                     text = ~paste(region))
```



# Table 1. Breastfeeding Practice Indicators

```{r, echo=FALSE}

library(DT)
datatable(subset(BAI, select=c(region, country, bf_1hour, bf_6months, bf_1yr, bf_2yr)), 
          colnames = c('Region', 'Country', '% breastfed  within an hour of birth', '% breastfed  exclusively for 6 months', '% breastfed at 1 year old', '% breastfed at 2 yrs old'), 
          filter = 'top', options = list(pageLength = 10, autoWidth = TRUE),
          caption = '')
```

